Outdated and License-Violating Code on Stack Overflow

### 2017-08-14 cloverflow-tse/cloverflow.tex
Latest update to the paper.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. 
% The archived dump has a size of 9 gigabytes. 
The data
dump is in XML format containing information of posts
(questions and answers) and 
% supporting data such as user accounts and timestamps of the posts.
we were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,332,940
lines\footnote{Measured by cloc:
	\url{https://github.com/AlDanial/cloc}} of Java source code.
The median of the snippet size is 10.
% excluding comments and blank lines.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrrr}
		\toprule
		Dataset & No. of files & SLOC & Median \\
		\midrule
		Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: }
We use clone detection to discover online code clones. 
%\textbf{Clone Detection and Configuration: } 
There are a number of restrictions in terms of choosing the clone
detection tools for this study. The main restriction is due to nature
of code snippets posted on Stack Overflow, as most of them are
incomplete Java classes or methods. Hence, a detector must be flexible
enough to process code snippets that are not compilable or not
complete blocks. Moreover, since the amount of code that has to be
processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to
report clones in a reasonable amount of time. We have tried 5
state-of-the-art clone detectors including Simian~\cite{simian},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
failed with execution errors after running for couple of hours. Thus,
we removed them from the study. Simian and NiCad are flexible enough
to handle code with incomplete methods or classes and successfully
completed the detection.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{NiCad} is also a text-based clone
detector which detects clones at either method- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and has also been used in several empirical clone
studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
	Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
pretty-printing source code and provides code normalisation by variable renaming
and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers
the same functionalities as the original NiCad but is specialised for detecting
code clones between two systems.

@@

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
	\small
	\begin{tabular}{p{0.8cm}|p{2.5cm}p{3.8cm}}
		\toprule
		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
		\midrule
		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\ 
		\bottomrule
		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
		\hline
	\end{tabular} %
%	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\toprule
		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
		\midrule
		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}

\subsection{Phase 2: Clone Filtering}
As there are in total 315,786,118 clone pairs reported, it is
infeasible for humans to manually validate them all. Instead of
investigating a random sample, we adopted the idea of \textbf{clone
	agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow Bellon's original definitions of
good- and ok-match~\cite{Bellon2007}, which are based on how much two
clone fragments \textit{CF} overlap\footnote{The overlap value can be
	considered as Jaccard similarity.}  and how much of them is
contained in each other:
%\squeezeup
\begin{displaymath}
overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{displaymath}
% \squeezeup
\begin{displaymath}
contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}
\noindent%
A clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
(\textit{CF$_1$}, \textit{CF$_2$}), and the \textit{good-value} and
the \textit{ok-value} of two clone pairs are defined as

@@

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\toprule
		Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
		\midrule
		\textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
		\textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
		\bottomrule
	\end{tabular} %
	% }
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|r}
		\toprule
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cmidrule{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\midrule 
		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
		\bottomrule
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

		UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
		\hline 
		BP & Boiler-plate or IDE auto-generated \\

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{classification_process}\vspace{-1ex}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\subsection{Stack Overflow Developers' Survey} We support our findings of
outdated and license-violating code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and licensing-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our \FIXME{technical
	report/website?} ~\footnote{Stack Overflow Answerers' Survey:
	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects for the different data sets}
	\label{tab:snippets}
	\centering
	\begin{tabular}{l|rrrr}
		\toprule 
		Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
		\midrule 
		\multicolumn{5}{l}{\textit{Reported Clones}} \\
		\midrule
		$S_D$ & 67,570 & 1,086 & 92 & 38\% \\
		$S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
		$N_D$ & 632,855& 1,392 & 88 & 30\% \\
		$N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
		\midrule
		Total & 315,786,118 & 14,856 & 111 & 38\% \\
		\midrule
		\multicolumn{5}{l}{\textit{Filtered Data Set}} \\
		\midrule
		\textit{good} & 2,313 & 97 & 67 & 23\% \\
		\textit{ok'} & 12,336 & 139 & 43 & 28\% \\
		$S_D'$ & 17,081 & 460 & 74 & 31\% \\
		$N_D'$ & 83 & 44 & 19 & 27\% \\
		\midrule
		Total & 32,533 & 623 & 96 & 27\%\\
		\midrule 
		%  \multicolumn{5}{l}{\textit{Filtered Data Set without AC}} \\
		%  \hline 
		%  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
		%  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
		%  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
		%  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
		%  \hline
		%  Total & 30,113 & 556 & 80 & 28\% \\
		%  \hline
		\multicolumn{5}{l}{\textit{True Positives in Manually Validated Clones}} \\
		\midrule 
		$\textit{good}/\textrm{AC}$ & 131 & 51 & 24 & 22\% \\
		$\textit{ok'}/\textrm{AC}$ & 152 & 83 & 22 & 21\% \\
		$S_D'/\textrm{AC}$ & 873 & 337 & 60 & 35\% \\
		$N_D'/\textrm{AC}$ & 60 & 33 & 15 & 27\% \\
		\midrule
		Total & 1,216 & 516 & 75 & 26\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}
	\centering
	\caption{No.~of online clones candidates for the classification}
	\label{tab:online_clone_classification_results}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrr}
		\toprule
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
		& & Auto & Manual \\
		\midrule 
		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\midrule
		Total  & 32,533 & 28,897 & 3,636 \\ 
		\bottomrule
	\end{tabular} %
	%}
\end{table}

\begin{table}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|rrrr|rrr|r}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
		\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
		\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
		\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
		\midrule
		Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
		\bottomrule
	\end{tabular} 
	%}
\end{table}

@@

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_exp_1-crop}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.82\linewidth]{survey_exp_2-crop}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow users}
	\label{fig:survey_exp}
\end{figure}

@@

\begin{figure*}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_snippet_source_1}
		\caption{Group 1}
		\label{fig:survey_snippet_source_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\linewidth]{survey_snippet_source_2}
		\caption{Group 2}
		\label{fig:survey_snippet_source_2}
	\end{subfigure}
	\caption{Sources of code snippets in Stack Overflow answers}
	\label{fig:survey_snippet_source}
\end{figure*}

@@

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Do you usually include a software license in your code snippets on Stack Overflow?}
	\label{fig:survey_license}
\end{figure}

@@

\subsubsection{License of Code Snippets} 
More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
of them do not include license statement in their code snippets (as depicted in
\Cref{fig:survey_license}) due to several reasons. First, some answerers posted
only their own code or code that was adapted from the question, hence
 they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
company or open source projects that they knew were permitted to be publicly distributed.
Third, some answerers believe that code snippets in their answers are too small 
to claim any intellectual property on them and fall under fair use.

>>>>

% The paper headers
\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, August~2017}%
{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Outdated and License-Violating Code on Stack Overflow}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
% The archived dump has a size of 9 gigabytes.
The data dump is in XML format containing information of posts (questions and
answers) and we were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are always displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
snippets of at least ten lines are usually more interesting since most of
boiler-plate code of \texttt{equal} or \texttt{hashCode} methods are removed.
Each snippet was extracted from the dump and saved to a file. Moreover, we
filtered out irrelevant code snippets that were part of the accepted answers
but were not written in Java by using regular expressions and manual checking.
~\FIXME{should I mention I use PMD CPD to help here? More confusing?}.
Finally we obtained
72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
	\url{https://github.com/AlDanial/cloc}} of Java source code. The median of the
snippet size is 10.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrrr}
		\toprule
		Dataset & No. of files & SLOC & Median \\
		\midrule
		Stack Overflow & 72,365 & 1,840,581 & 10 \\ 
		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution. Although Simian, SourcererCC,
CCFinder, iClones, and DECKARD could successfully report clones, we decided to
choose Simian and SourcererCC due to their fast detection speed.

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
detector which detects clones at either function- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and offer scalability against large code
corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Due to incomplete code blocks and
functions normally found in Stack Overflow snippets, the built-in Java tokeniser
could not parse more than half of all snippets. SourcererCC provides an option
to plug in a customised tokeniser, so we developed a special Java tokeniser with
assistance from the tool's creator. Another benefit of SourcererCC is its
indexing and search processing allows us to detect code clones between two
systems.

@@

\begin{table}
	\centering
	\caption{Configurations of Simian and SourcererCC}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
	\small
	\begin{tabular}{lp{5cm}}
		\toprule
		Tool & Configurations \\
		\midrule
		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
		\midrule
		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
		\bottomrule
	\end{tabular} %
%	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian and SourcererCC}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrr}
		\toprule
		Stats & \multicolumn{1}{c}{Simian} & \multicolumn{1}{c}{SourcererCC} \\
		\midrule
		Total clone pairs & 721 & 1,678 \\
		Average clone size & 16.61 & 17.86 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}

\subsection{Phase 2: Clone Merging}
As there are in total 315,786,118 clone pairs reported, it is
infeasible for humans to manually validate them all. Instead of
investigating a random sample, we adopted the idea of \textbf{clone
	agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow Bellon's original definitions of
good- and ok-match~\cite{Bellon2007}, which are based on how much two
clone fragments \textit{CF} overlap\footnote{The overlap value can be
	considered as Jaccard similarity.}  and how much of them is
contained in each other:
%\squeezeup
\begin{displaymath}
overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{displaymath}
% \squeezeup
\begin{displaymath}
contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
\end{displaymath}
\noindent%
A clone pair \textit{CP} is formed by two clone fragments
\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
(\textit{CF$_1$}, \textit{CF$_2$}), and the \textit{good-value} and
the \textit{ok-value} of two clone pairs are defined as

@@

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrr}
		\toprule
		Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
		\midrule
		\textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
		\textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
		\bottomrule
	\end{tabular} %
	% }
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrccr}
		\toprule
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c}{Filters*} & \multirow{2}{*}{After Filtering} \\ %\cmidrule{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\midrule 
		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
		\bottomrule
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

		UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
		\midrule
		BP & Boiler-plate or IDE auto-generated \\

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{classification_process}\vspace{-1ex}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\subsection{Stack Overflow Developers' Survey} We support our findings of
outdated and license-violating code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and licensing-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our \FIXME{technical
	report/website?} ~\footnote{Survey--Stack Overflow Answerers:
	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.

@@

\begin{table}
	\caption{Investigated online clone pairs and corresponding snippets
		and Qualitas projects}
	\label{tab:snippets}
	\centering
	\begin{tabular}{rrrr}
		\toprule
		Pairs & Snippets & Projects & Avg.~cloned ratio \\
		\midrule
		2,304 & 460 & 77 & ??\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
		\bottomrule
	\end{tabular}
\end{table}

@@

%\begin{table}
%	\centering
%	\caption{No.~of online clones candidates for the classification}
%	\label{tab:online_clone_classification_results}
%	%\small
%	%	\resizebox{\columnwidth}{!}{%
%	\begin{tabular}{lrrr}
%		\toprule
%		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
%		& & Auto & Manual \\
%		\midrule 
%		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
%		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
%		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
%		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
%		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
%		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
%		\midrule
%		Total  & 32,533 & 28,897 & 3,636 \\ 
%		\bottomrule
%	\end{tabular} %
%	%}
%\end{table}

\begin{table}
	\centering
	\caption{Classifications of online clone pairs.}
	\label{tab:classification_good_o}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{lrrrrrrrr}
		\toprule
		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
		\midrule
		\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
		\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
		\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
		\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
		\midrule
		Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
		\bottomrule
	\end{tabular} 
	%}
\end{table}

@@

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_exp_1-crop}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.62\linewidth]{survey_exp_2-crop}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow users}
	\label{fig:survey_exp}
\end{figure}

@@

\begin{figure*}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_snippet_source_1}
		\caption{Group 1}
		\label{fig:survey_snippet_source_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.8\linewidth]{survey_snippet_source_2}
		\caption{Group 2}
		\label{fig:survey_snippet_source_2}
	\end{subfigure}
	\caption{Sources of code snippets in Stack Overflow answers}
	\label{fig:survey_snippet_source}
\end{figure*}

@@

\begin{figure}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Software license in Stack Overflow code snippets.}
	\label{fig:survey_license}
\end{figure}

@@

We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in their answers (see \Cref{fig:survey_outdated}). The ratio drops to 47.6\% in
Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
are aware of their outdated code in some of their answers.

\begin{figure}
	\centering
	\includegraphics[width=.8\linewidth]{survey_outdated}
	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
	\label{fig:survey_outdated}
\end{figure}%

We then asked the participants to have been notified of their outdated code
(80 and 48 participants from Group 1 and 2 respectively) a
follow-up questions ``how frequently did you fix your outdated code on Stack
Overflow?''. The answers, depicted in \Cref{fig:survey_outdated_fix}, show that
more than half of them frequently fix the outdated code snippets. However, there
are 18.8\% of the answerers in both groups who rarely or never fix their code.
